\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-11-08 jss/article.tex
edit

In the other two cases, Poisson and Binomial, the flat prior distribution on $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($\pi(B_{j})\propto B_{j}^{-2} d B_j$) as does $A$ with Uniform($0, \infty$) for the Gaussian. As for the posterior propriety, we found that the resultant posterior distribution for the Binomial model is proper if there are at least two groups (among $k$ groups), whose observed values ($z_{j}$) are neither 0 nor $n_j$,  and the covariate matrix ($X_{(k\times m )}$), if any,  has a full rank ($rank(X)=m$). 
\\

>>>>

In the other two cases, Poisson and Binomial, the flat prior distribution on $\frac{1}{r}$ induces the same improper prior distribution on shrinkages ($\pi(B_{j})\propto B_{j}^{-2} d B_j$) as does $A$ with Uniform($0, \infty$) for the Gaussian. As for the posterior propriety, we found that the resultant posterior distribution for the Binomial model is proper if there are at least two groups (among $k$ groups), whose observed values ($z_{j}$) are neither 0 nor $n_j$,  and the covariate matrix ($X_{(k\times m )}$), if any,  has full rank ($rank(X)=m$). 
\\
